% (500 words)
%LEITFADEN:
% Die Einleitung dient der Einführung in das Thema, indem eine spezifische Fragestellung (For- schungsfrage) herausgearbeitet, plausibel formuliert, differenziert und begründet wird. Die methodische Vorgehensweise („Wie wird das Thema bearbeitet?“) muss begründet und auf das Thema und die Frage- und Problemstellung der Arbeit bezogen werden. Des Weiteren sollte in der Einleitung oder in einem gesonderten Kapitel (Verwandte Arbeiten) die zur Bearbeitung herangezogene wissenschaftliche Literatur sowie die spezifische Auswahl von Quellen und Texten dargestellt und erläutert werden.





%TODO: also add a paper on eating crises...
% the book
\textcite{han2011data}[18, 32, 362, 363, 367] declare, that data mining is used to discover patterns and knowledge from data.
% (17) This includes cleaning data, combining multiple sources, selecting and transforming relevant data, and extracting and evaluating data patterns.
Cluster Analysis is a type of machine learning algorithm known as unsupervised machine learning. It is used in data mining to divide data into groups (clusters). Each cluster contains data that is similar to each other, but dissimilar to the data allocated to other clusters. Cluster Analysis can be used to acquire knowledge on the distribution of the data, discover characteristics, detect outliers and reduce noise, or to pre-process data for other algorithms. 

There are several different methods to create clustering. \textcite{han2011data}[364, 366-367, 374, 385, 392] explain, that objects are often arranged into clusters using distance measures (e.g. Euclidean or Manhatten distance measures). 
The authors divide the clustering algorithms into the following categories:
\begin{itemize}
	\item Partitioning methods (examples: k-means, k-medoids)
	\item Hierarchical methods (examples: BIRCH, Chameleon)
	\item Density-based methods (examples: DBSCAN, OPTICS)
	\item Grid-based methods (examples: STING, CLIQUE)
\end{itemize}


%Related work
%Evidence Analysis to Basis of Clustering
% \textcite{forensics} introduce in their paper, how clustering can be used in digital forensics to provide information on all the events that led up to a certain crime. They used ascending hierarchical clustering to receive clusters of events (e.g. phone calls, SMS) ordered in time, thus creating a timeline of events leading up to the incident.
% The idea was by using a hierarchical fusion process, it would be possible to create a chain of events 

%Convex-Hull & DBSCAN Clustering to Predict Future Weather
% Another example where clustering was implemented was by /textcite. 
% \textcite{convexhullDbscan}[1,2,6,7] give an example, where clustering was implemented to predict future weather. Air pollutant data was preprocessed and then arranged into clusters using (incremental) DBSCAN clustering. Finally, priority based protocol was used on them to predict weather conditions and a temperature range. The accuracy of the technique, based on hit and miss times, was calculated to approximately 74.5\%.

%end related work

% Talk about SmartEater.
SmartEater \footnote{\url{https://sites.google.com/site/eatingandanxietylab/resources/smarteater}} is an upcoming mHealth (mobile health) app, with the goal to provide the user with content-dependent feedback, to avert a food craving episode. The app will predict future eating crises based on the user's past behaviour. In order to reduce intense user input, the app records and uses various smartphone sensor data. With the help of data mining, machine learning algorithms, and pattern recognition, this recorded situational context data will aid in predicting stress. The following data is recorded by the app:

\begin{enumerate}
	\item Movement of the smartphone (accelerometer)
	\item Volume of the audio
	\item Percentage of screen on time
	\item Number of notifications
	\item Light sensor values
	\item App usages in the categories communication, video players, and other
\end{enumerate}



%cite smarteater website  - as footnote
This sensor data was recorded for different lengths of time on different test subjects and aggregated to 1 hour and 3 hour files. It is necessary to establish which time period will be most fitting to make accurate predictions for the future. This thesis will use cluster analysis to determine which time period is most significant.

According to \textcite{han2011data}[414], the above-mentioned clustering methods work well with datasets that are not high-dimensional and have less than 10 attributes. Since the SmartEater dataset only has 8 unique dimensions (columns), it is not considered high-dimensional. This paper will therefore utilise these clustering methods. Since different clustering algorithms can yield different results, multiple methods will be used and compared.

%book page 93
To reduce the size and amount of data, dimensionality reduction will be used. \textcite{han2011data}[93] define dimensionality reduction as a type of data reduction, which removes random attributes and creates a smaller dataset with close to equal integrity. This thesis will compare principal component analysis (PCA) and t-SNE to reduce the dimensionality.
% %Visualizing Data using t-SNE p2579 (abstract!)
% Furthermore, T-Distributed Stochastic Neighbor Embedding (t-SNE) will be employed to depict the dataset in this thesis. \textcite{maaten2008visualizing}[2579] first introduce t-SNE, which is used to visualise data with a higher dimensionality. 

%ies Pandas\footnote{\url{https://pandas.pydata.org}} and
The clustering methods will be implemented using the Python machine learning platform (e.g. Anaconda\footnote{\url{https://www.anaconda.com/}}), with the library scikit-learn\footnote{\url{https://scikit-learn.org/stable/}}. These will be implemented on all the time lengths. The resulting clusters of each time length will be compared to one another and evaluated. 
\textcite{rousseeuw1987silhouettes} reveals how silhouettes can be used to measure the separation between clusters and therefore evaluate the quality of the resulting clusters are. Other mathematical evaluation scores used are Davies-Bouldin Index (\textcite{DaviesBouldin}) and Caliński-Harabasz Index (\textcite{calinskiHarabasz}).

% Evaluation examples given by \textcite{han2011data}[396-399] include clustering tendency, intrinsic and extrinsic measurements. 



The thesis will be structured as follows: Section \ref{section:RelatedWork} will briefly present existing work relating to this subject. The following chapter, section \ref{section:Theory}, will concentrate on the theory of data mining and cluster analysis. After covering these topics, section \ref{section:Experiment} will describe the conducted experiment and its results. In the final sections, the findings of the experiment will be discussed and summarised. 


% \textbf{TODO: !!!WRITE ABOUT EATING DISORDERS..!!, ALSO WRITE ABOUT MOBILE HEALTH APPS} 
%TODO: from smartphone based stress prediction (paper bei stütz, ginzinger):
% Stress has become a major concern, as stress-related diseases cause a decrease in life expectancy and in the quality of life, as well as an increase in the number of sick leaves. Stress is a risk factor for a multitude of diseases, also because stress is closely linked to unhealthy behaviour, such as excessive consumption of food and alcoholic beverages [1,21].
%1: 1. Adam, T.C., Epel, E.S.: Stress, eating and the reward system. Physiology & behavior 91(4), 449–458 (2007)
%21: 21. Schwabe, L., Dickinson, A., Wolf, O.T.: Stress, habits, and drug addiction: a psychoneuroendocrinological perspective. Experimental and clinical psychopharmacology 19(1), 53 (2011)

%e.g. like: Predicting “About-to-Eat” Moments for Just-in-Time Eating Intervention
%Snoring paper abstract: Mobile Health broadens the accessibility to healthcare applications using mobile devices, such as smartphones.

